Incentivizing Exploration by Heterogeneous Users

### 2018-06-06 algorithm_regret.tex
marked using bcedit

Adding all four types of regret terms,
and substituting 
$\EarlyCut[2]{s} = \frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$,
the cumulative regret up to time $T$ is at most
$
O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
+ \ARMNUM \MAXR \log^2(T)
+ \frac{\ARMNUM \MAXR d}{T}
+ \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} \EarlyCut[2]{s} \log(s) \right)\\
= 
O \left(\ARMNUM  \cdot \exp \left( \frac{2}{p} \right)
+ \ARMNUM \TieDensity \cdot \log^3(T) \right)$.\QED
\end{emptyextraproof}

>>>>

Adding all four types of regret terms,
and substituting 
$\EarlyCut[2]{s} = \frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$,
the cumulative regret up to time $T$ is at most
$
O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
+ \ARMNUM \MAXR \log^2(T)
+ \frac{\ARMNUM \MAXR d}{T}
+ \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} \EarlyCut[2]{s} \log(s) \right)\\
= 
O \left(\ARMNUM  \cdot \exp \left( \frac{2}{p} \right)
+ \bcedit{\ARMNUM \log^2(T)} + \ARMNUM \TieDensity \cdot \log^3(T) \right)$.\QED
\end{emptyextraproof}

### 2018-06-06 introduction.tex
marked using bcedit

\begin{theorem} \label{thm:main-intro}
Assume that for each arm, at least a constant fraction \MinProb
of the population likes this arm best,
and let \TieDensity be a measure of the ``density of near-ties''
between agents' arm preferences
(in a sense made precise in Section~\ref{sec:prob}).
There is a policy that achieves expected 
cumulative regret $O (\ARMNUM \e^{2/\MinProb} + \TieDensity \ARMNUM \log^3(T))$,
using expected cumulative payments of $O(\ARMNUM^2 \e^{2/\MinProb})$.
In particular, when agents who are close to tied between two arms have measure $0$,
both the expected regret and expected payment are bounded by constants
(with respect to $T$). 
\end{theorem}

>>>>

\begin{theorem} \label{thm:main-intro}
Assume that for each arm, at least a constant fraction \MinProb
of the population likes this arm best,
and let \TieDensity be a measure of the ``density of near-ties''
between agents' arm preferences
(in a sense made precise in Section~\ref{sec:prob}).
There is a policy that achieves expected 
    cumulative regret $O (\ARMNUM \e^{2/\MinProb} + \bcedit{\ARMNUM \log^2(T)} + \TieDensity \ARMNUM \log^3(T))$,
using expected cumulative payments of $O(\ARMNUM^2 \e^{2/\MinProb})$.
\end{theorem}

### 2018-06-06 result_discussion.tex
marked using bcedit

\begin{theorem} \label{rst:regret}
For any time horizon $T$, the expected cumulative regret for
Algorithm~\ref{alg:basic-incentivizing} up to time $T$ is bounded
above by 
$O \left(\ARMNUM \cdot \e^{2/\MinProb} + \TieDensity \ARMNUM \log^3(T) \right)$.
\end{theorem}

@@

The fact that constant regret can be achieved with constant payment
(independent of $T$) when $\TieDensity = 0$ suggests aiming for a
constant bound more generally, i.e., for $\TieDensity > 0$.
That such a bound is unachievable is shown in Appendix~\ref{sec:lb},
where we show a lower bound of $\Omega(\log(T))$ on
the expected regret of any algorithm.
The instance is simple: it has two arms, one \pfedit{with known}
attributes; 
in addition, one draw from the other arm is observed in
each step $t$ even when it is not pulled.
While the probability of pulling the wrong arm decreases over time, it
does not do so fast enough, causing the stated regret.

>>>>

\begin{theorem} \label{rst:regret}
For any time horizon $T$, the expected cumulative regret for
Algorithm~\ref{alg:basic-incentivizing} up to time $T$ is bounded
above by 
    $O \left(\ARMNUM \cdot \e^{2/\MinProb} + \bcedit{\ARMNUM \log^2(T)}+ \TieDensity \ARMNUM \log^3(T) \right)$.
\end{theorem}

@@

The fact that constant regret can be achieved with constant payment
(independent of $T$) when $\TieDensity = 0$ suggests aiming for a
constant bound more generally, i.e., for $\TieDensity > 0$.
That such a bound is unachievable is shown in Appendix~\ref{sec:lb},
where we show a lower bound of $\Omega(\log(T))$ on
the expected regret of any algorithm.
The instance is simple: it has two arms, one with known attributes; 
in addition, one draw from the other arm is observed in
each step $t$ even when it is not pulled.
While the probability of pulling the wrong arm decreases over time, it
does not do so fast enough, causing the stated regret.
